
\label{app:contributions}

\noindent\textbf{Data collection and operations}. Ashwin Balakrishna, George Bokinsky, Thomas Charbonnier, Grace Connors, Michael Equi, Chelsea Finn, Lachlan Groom, Hunter Hancock, Karol Hausman, Connor Jacobsen, Rowan Jen, Marinda Lamb, Vishnu Mano, Nandan Marwaha, Aikys Mongush, Tyler Patterson, Charvi Sharma, Lucy Xiaoyang Shi, Laura Smith, Will Stoeckle, Anna Walling, Jason Wang, Samuel Whitmore, Blake Williams.

\noindent\textbf{Annotation and supplemental data.}. Ashwin Balakrishna, Karan Dhabalia, Danny Driess, Chelsea Finn, Haroun Habeeb, Rowan Jen, Chandra Kuchi, Karl Pertsch, Lucy Xiaoyang Shi, Will Stoeckle, Quan Vuong.

\noindent\textbf{Policy training and research.}. Bo Ai, Ashwin Balakrishna, Kevin Black, Danny Driess, Michael Equi, Yunhao Fang, Chelsea Finn, Catherine Glossop, Haroun Habeeb, Karol Hausman, Gashon Hussein, Victor Hwang, Brian Ichter, Liyiming Ke, Sergey Levine, Xinyu Li, Yao Lu, Suraj Nair, Karl Pertsch, Allen Z. Ren, Baifeng Shi, Lucy Xiaoyang Shi, Laura Smith, Jost Tobias Springenberg, Kyle Stachowicz, Jiaming Tang, Marcel Torne, Kyle Vedder, Quan Vuong, XuDong Wang, Charles Xu, Lili Yu, Wuming Zhang, Zhuoyang Zhang.

\noindent\textbf{Policy infrastructure.}. Kevin Black, Karan Dhabalia, Danny Driess, Mairbek Khadikov, Chandra Kuchi, Adrian Li-Bell, Vladislav Lialin, Wallace Lim, Yao Lu, Allen Z. Ren, Lucy Xiaoyang Shi, Kyle Stachowicz, Jiaming Tang, Quan Vuong, Haohuan Wang, Ury Zhilinsky.

\noindent\textbf{Robot hardware.}. Ali Amin, Raichelle Aniceto, Greg Balke, Vedant Choudhary, Foster Collins, Grace Connors, Maitrayee Dhaka, Adnan Esmail, Thomas Godden, Ivan Goryachev, Tim Jones, Gregg Kammerer, Ben Katz, Devin LeBlanc, Brendon LeCount, Zhonglin Liang, Enyu Luo, Liam Murphy, Gavin Schelske, Shalom Tekeste, Chris Whalen, Sukwon Yoo.

\noindent\textbf{Robot infrastructure}. Greg Balke, Kevin Black, Shihao Cao, Ken Conley, James Darpinian, Jared DiCarlo, Hunter Hancock, Karol Hausman, Szymon Jakubczak, Jimmy Tanner.

\noindent\textbf{Writing and illustration.}. Bo Ai, Ashwin Balakrishna, Kevin Black, Chelsea Finn, Sergey Levine, Allen Z. Ren, Lucy Xiaoyang Shi, Laura Smith, Kyle Stachowicz.

