
\label{app:tasks}

\noindent \textbf{Laundry (T-shirts and Shorts).} Fold a single pair of shorts or a T-shirt taken from a laundry basket into a compact, neatly aligned fold and place/stack it appropriately.
Scoring: success if successfully folding the item and properly stacking it on top of other laundry.

\noindent \textbf{Laundry (Diverse --- Hardest Item).} Fold a single buttonup shirt taken from a laundry basket into a compact, neatly aligned fold and place/stack it appropriately. Scoring: success if successfully folding the item and properly stacking it on top of other laundry.

\noindent \textbf{Make Espresso.} Execute an espresso workflow to prepare and extract a doppio (double espresso) with correct sequencing and placements.
Scoring: success if completing the required steps in order: grounds dispensed and tamped, portafilter locked into the correct grouphead, extraction performed, cup placed on saucer and moved right.

\noindent \textbf{Box Building.} Assemble a flat box into a 3D box. Scoring: success if the box is folded correctly without major damage.

\noindent \textbf{Make Peanut Butter sandwich.} Make a peanut-butter sandwich, cut it diagonally all the way through, and present it on the plate; close the peanut butter jar; push the plate away.
Maximum score: 9. Points awarded for: removing the jar lid; progressively spreading peanut butter coverage; placing the plain slice on top; cutting diagonally fully through; placing the knife back on the plate; pushing the plate away; and overall neatness.

\noindent \textbf{Turn a T-shirt Inside Out.} Retrieve an inside-out t-shirt, turn it fully right-side-out (torso + both sleeves), fold it into a compact form.
Maximum score: 7. +1 retrieve shirt; +1 torso right-side-out; +1 left sleeve right-side-out; +1 right sleeve right-side-out; +1 compact fold; +1 placed on pile; +1 positioned in upper-right corner.

\noindent \textbf{Drive Through Door.} Open a self-closing closet door, drive the robot fully inside, and finish with the door closed and the robot inside.
Maximum score: 3. +1 for opening the door; +1 for driving far enough inside for the door to close; +1 for smooth entry without bumping into the doorway.

\noindent \textbf{Cut Zucchini.} Slice a zucchini into thin slices using a knife attached to a lanyard while stabilizing the zucchini with the opposite gripper.
Maximum score: 3. +1 for successfully picking up the knife correctly; +1 for fully cutting the zucchini into thin, even slices; +1 for safely returning the knife to the right side of the cutting board.

\noindent \textbf{Peel Fruits and Vegetables.} Peel a fruit/vegetable completely by holding the item against cutting board, and peeling it with the other gripper.
Maximum score: 9. +1 for picking up the peeler; +1 for peeling up to 25\%; +1 for peeling 25–50\%; +1 for peeling 50–75\%; +1 for peeling $>$75\%; +1 for putting the fruit/veg into the bowl; +1 for scraping 25–50\% of food scraps into the trash can; +1 for scraping 50–75\% of food scraps into the trash can; +1 for scraping $>$75\% of food scraps into the trash can.

\noindent \textbf{Take Out Trash.} Remove an old trash bag, place it away from the bin, line the trash can with a new bag, and return the bin to its home location (and close the cabinet / replace lid as appropriate). Maximum score: 12. Taking out trash can (3 points): +2 if the robot correctly accesses the trash can (opens the under-sink cabinet door); +1 if the robot relocates the trash can from under the sink to an accessible position on the kitchen floor. Remove from bin (3 points): +1 if the robot pulls the trash bag away from the corners of the bin; +1 if the robot gathers and securely lifts the trash bag out of the bin; +1 if the robot removes the trash bag from the bin and places it on the floor near the trash can. Replace bag (3 points): +1 if the robot picks up the replacement trash bag; +1 if the robot opens the replacement bag; +1 if the robot places the replacement trash bag fully inside the trash can and stretches the edges securely around the rim. Return trash can back (3 points): +2 if the robot lifts and returns the trash can to the under-sink cabinet; +1 if the robot closes the cabinet door fully at the end of the episode.


\noindent \textbf{Swap 3 Mugs.} Sequentially place three mugs onto a coffee machine drip tray (one at a time), ensuring each mug occupies the tray once, with mugs returned to the table between placements as required. Maximum score: 4. +1 for removing mug 1 from the coffee maker and placing it on the table; +1 for placing mug 2 from the table onto the coffee maker; +1 for removing that same mug 2 from the coffee maker and placing it on the table; +1 for placing the remaining mug 3 from the table onto the coffee maker.

\noindent \textbf{Find Object.} Retrieve an object hidden in a drawer and restore a clean final scene (object on table, drawers closed).
Maximum score: 4. +1 for fully opening the target drawer with the item on the first try; +1 for picking up the sponge stick; +1 for placing the sponge stick on the table (anywhere); +1 for closing the opened target drawer.


\noindent \textbf{Scoop Beans.} Scoop exactly two scoops of coffee beans into a grinder using a measuring cup, then close the grinder lid. Maximum score: 5. +1 for opening the coffee grinder; +1 for grasping the scoop; +1 for successfully collecting and pouring the first full scoop of beans into the coffee grinder; +1 for successfully collecting and pouring the second full scoop of beans into the coffee grinder; +1 for closing the coffee grinder lid.

\noindent \textbf{Window Cleaning.} Spray the phone booth window with windex, rip a paper towel, wipe the glass fully dry, and discard the towel. Maximum score: 5. +1 for spraying the booth; +1 for getting the paper towel for cleaning; +1 for cleaning overall the whole door and leaving it dry; +1 for throwing the paper towel in the trash can; +1 for not leaving any drops left on the door.

\noindent \textbf{Reverse Bussing.} Sort 12 objects with reversed mapping: place trash into the bussing bin and dishes/utensils into the trash can. Maximum score: 12. +1 for successfully putting a plate, cup, bowl, or utensil in the trash (7 total); +1 for successfully putting a plastic bottle, foil, plastic lid, take out container, or chip bag in the bussing bin (5 total).

\noindent \textbf{Reverse Fridge to Microwave.} Move a plate of (real) frozen microwavable food from the microwave into the refrigerator (reverse sequence version), and complete the episode with the plate stored in the fridge.
Maximum score: 6. +1 for microwave door opening; +1 for microwave door closing; +1 for plate removed from microwave; +1 for plate placed in refrigerator; +1 for refrigerator door opening; +1 for refrigerator door closing.

\noindent \textbf{Table Setting.} Set a table by placing a placemat, cup, plates, napkin, and utensils from a bin into a reasonable table setting.
Maximum score: 7. +1 per item successfully placed; critically incorrect placements can be scored as -1.

\noindent \textbf{Bag in Backpack.} Place a small pouch/bag into a backpack (no need to zip closed).
Maximum score: 3. +1 pick up pouch; +1 grasp backpack; +1 place pouch inside backpack.

\noindent \textbf{Organize Tupperware.} Nest three tupperware containers (descending sizes) and stack their corresponding lids.
Maximum score: 6. +1 for each container correctly nested; +1 for each lid correctly stacked/aligned.

\noindent \textbf{Shirt Bagging.} Place two shirts fully inside a brown grocery bag (per-scene), optionally using language commands with timing-sensitive instruction handoff.
Maximum score: 4. +1 for correct pick for each shirt; +1 for each shirt fully placed inside the bag.

\noindent \textbf{Shirt Folding.} Fold a single t‑shirt from a flattened start state into a folded end state.
Maximum score: 6. +1 for completing the first fold (grasp cloth with both arms; folded edge aligned with intended fold within 5 inches); +1 for completing the second fold (same criterion); +1 for completing the final fold (completed with right arm; aligned within 5 inches); plus a fold quality score from 0–3 based on the final folded state chart. Full score of 6 is considered success.

\noindent \textbf{Press French Press Plunger.} Press the french press plunger fully down to the bottom.
Maximum score: 1. +1 if the robot manages to press the plunger down to the bottom (through coffee).

\noindent \textbf{Scoop Rice into Rice Cooker.} Pick up a rice scooper from a rice container, scoop rice, and pour it into an open rice cooker.
Maximum score: 3. +1 pick up scooper; +1 scoop rice; +1 pour into cooker.

\noindent \textbf{Loading an Air Fryer.} Open an air fryer, place a sweet potato into the basket, and close the air fryer.
Maximum score: 4. +1 open air fryer; +1 pick up sweet potato; +1 place into air fryer; +1 close air fryer.

\noindent \textbf{Unloading an Air Fryer.} Pull out an air fryer basket and dump 8 fake fries onto a plate. Maximum score: 2. +1 if the robot successfully picks up all food items from the air fryer; +1 if the robot places all food items onto the plate.

\noindent \textbf{Toast a Bagel.} Place a sliced half-bagel into a toaster oven, initiate toasting by turning the knob, then retrieve and serve it on a plate taken from an overhead cabinet.
Maximum score: 7 (open oven; insert bagel; close oven; turn knob; retrieve plate; retrieve toast; place on plate).

\end{document}
